Manuscript Figures for Genome Biology

### 2018-04-30 manuscript_figures/mansuscript_figures.Rmd
Add Figure 4 prototype

This is a heatmap of methods by case studies with color representing the ranking
by of number of rejections @ FDR cutoff 0.05.

```{r, Figure 4}
# TO DO
```

>>>>

This is a heatmap of methods by case studies with color representing the ranking
by of number of rejections @ FDR cutoff 0.10.

```{r, Figure 4}
library(SummarizedBenchmark)
library(stringr)
library(viridis)

outdir <- "casestudy-figs"
dir.create(outdir, showWarnings = FALSE)

# assumes sb objects are in the following location, which contains subfolders
# for each casestudy (if this isn't true, then parsing the case study and 
# dataset names later on will be incorrect)
path <- "../../sb-objects/"
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
alpha <- 0.10

# remove simulation objects
sim <- unique(c(which(grepl("simulations", objects)),
               which(grepl("yeast", objects)),
               which(grepl("polyester", objects))))

if (length(sim) > 0){
  objects <- objects[-sim]
}

# create tidy data frame where each row is a method / dataset observation
# of a rank 
ranks <- data.frame()
obj.names <- str_split(objects, pattern = "/")
casestudy <- unlist(lapply(obj.names, function(x) x[5] ))
dataset <- unlist(lapply(obj.names, function(x) x[6] ))

for (i in seq_along(objects)){
  x <- readRDS(objects[i])
  assayNames(x) <- "qvalue"
  x <- addDefaultMetrics( x )

  hasResults <- apply(!is.na( assays(x)[["qvalue"]] ), 2, all )

  tmp <- estimatePerformanceMetrics(x, alpha, tidy=TRUE) %>%
    filter( performanceMetric == "rejections") %>%
    rename( method = blabel) %>%
    filter( is.na(param.alpha) | (param.alpha == alpha)) %>%
    filter( is.na(param.smooth.df) | (param.smooth.df == "3L")) %>%
    filter( !method == "unadjusted") %>%
    select( method, value ) %>%
    rename( nrejects = value) %>%
    mutate( method = gsub("-df03", "", method)) %>%
    mutate( method = gsub("-a10", "", method)) %>%
    na.omit() %>%
    mutate( rank = rank(nrejects) / n() ) %>%
    mutate(casestudy = casestudy[i],
           dataset = dataset[i])

  ranks <- rbind(ranks, tmp)
}

# average over datasets within case study
ranks_avg <- ranks %>% 
  group_by( casestudy, method) %>%
  summarize( mean_rank = mean(rank, na.rm = TRUE))

# heatmap : rows method, cols casestudy
Fig4 <- ggplot(ranks_avg, aes(x = casestudy, y = method, fill = mean_rank)) + 
  geom_raster() + 
  scale_fill_viridis() +
  theme_bw() +
  xlab("Case Study") +
  ylab("Method") +
  labs(fill = "Mean rank")

Fig4
ggsave(file.path(outdir, "Figure4.pdf"), width=6, height=4, dev = pdf)
```
